A JSDM with zero-inflation to increase the ecological relevance of analyses of species distribution data.

### 2025-07-24 PAPER_CODE.qmd
Update PAPER_CODE.qmd

---
title: "A JSDM with zero-inflation to increase the ecological relevance of analyses of species distribution data."
author: "Jeanne Tous, Julien Chiquet, Amy E. Deacon, Ada Fontrodona-Eslava, Douglas F. Fraser, Anne E. Magurran"
format: html
editor: visual
---

>>>>

---
title: "A JSDM with zero-inflation to increase the ecological relevance of analyses of species distribution data."
author: 
format: html
editor: visual
---
